aodc

### 2024-02-05 writing/paper_aodc.qmd
Use an approximate solar time for `seconds.since.midnight`.
Added AODC error envelopes.

```{r}
source.files = "globals libraries util data modeling paper_functions"
for (filename in strsplit(source.files, " ")[[1]])
    source(sprintf("code/%s.R", filename))
suppressPackageStartupMessages(
    library(flextable))
```

@@

```{r}
#| label: tbl-cv-hour
#| tbl-cap: Performance by hour of the day.
flextable(pretty.table.numbers(d[,
    keyby = .(Hour = hour(lubridate::with_tz(time.sat, "Etc/GMT+6"))),
    eval(performance.j)]))
```

@@

>>>>

```{r}
source.files = "globals libraries util data modeling paper_functions"
for (filename in strsplit(source.files, " ")[[1]])
    source(sprintf("code/%s.R", filename))
suppressPackageStartupMessages(
    library(flextable))
IG = knitr::include_graphics
```

@@

```{r}
#| label: tbl-cv-hour
#| tbl-cap: Performance by hour of the day.
flextable(pretty.table.numbers(d[,
    keyby = .(Hour = seconds.since.midnight %/% (60L * 60L)),
    eval(performance.j)]))
```

@@

## Error envelopes

We use … The results are an envelope with `r eee = \(pred) {o = empirical.error.envelope(obs = d$y.ground, pred); stopifnot(o$convergence == 0); o$par}; show.eee = \(pred) {ps = eee(pred); sprintf("additive part %.03f and multiplicative part %.03f", ps[1], ps[2])}; show.eee(d$y.sat)` for the raw satellite values, and an envelope with `r show.eee(d$y.ground.pred)` for our predictions. The mean widths of the envelopes across all observations are `r me = \(pred) {ps = eee(pred); sprintf("%.03f", 2*ps[1] + 2*ps[2]*mean(d$y.ground))}; me(d$y.sat)` for the raw values and `r me(d$y.ground.pred)` for our predictions.

```{r agreement_plot}
#| label: fig-agreement-plot
#| fig-cap: !expr caption
caption = with(list(d = agreement.plot.data(d)), sprintf(
    "Agreement plots for satellite-based and AERONET AOD. Straight lines show empirical error envelopes containing 2/3 of retrievals. Not shown: %s %s and %s %s",
    d[!in.region & comparison == "y.sat", .N],
    "points outside left panel",
    d[!in.region & comparison == "y.ground.pred", .N],
    "points outside right panel"))
IG(tar_read(agreement.plot.path))
```
